Appendix

### 2020-04-29 appendix/appendixV5.Rmd
Regression tables. Centering Kable tables.

kable(aux)

@@

kable(mod1)

@@

kable(mod1_permu)

@@

kable(mod2)

@@

kable(mod2_permu)

@@

kable(mod3)

@@

kable(mod3_permu)

@@

kable(mod4)

@@

kable(mod4_permu)

@@

kable(mod5)

@@

kable(mod5_permu)

@@

kable(mod5_permu)

@@

kable(mod5_permu)

@@

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

@@

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

@@

```{r}
permutest(mod, progbar = F)
```

>>>>

kable(aux) %>%
  kable_styling(position = "center")

@@

kable(mod1) %>%
  kable_styling(position = "center")

@@

kable(mod1_permu) %>%
  kable_styling(position = "center")

@@

kable(mod2) %>%
  kable_styling(position = "center")

@@

kable(mod2_permu) %>%
  kable_styling(position = "center")

@@

kable(mod3) %>%
  kable_styling(position = "center")

@@

kable(mod3_permu) %>%
  kable_styling(position = "center")

@@

kable(mod4) %>%
  kable_styling(position = "center")

@@

kable(mod4_permu) %>%
  kable_styling(position = "center")

@@

kable(mod5) %>%
  kable_styling(position = "center")

@@

kable(mod5_permu) %>%
  kable_styling(position = "center")

@@

kable(mod6) %>%
  kable_styling(position = "center")

@@

kable(mod6_permu) %>%
  kable_styling(position = "center")

@@

\newpage

## Summary of Models

### Summary of Base Models

```{r}
aux = bind_rows(
  mod1,
  mod3,
  mod5
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

### Summary of Base Models (Permutation)

```{r,echo=F}
aux = bind_rows(
  mod1_permu,
  mod3_permu,
  mod5_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

### Summary of Models with all coefficients

```{r,echo=F}
aux = bind_rows(
  mod2,
  mod4,
  mod6
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

### Summary of Models with all coefficients (Permutation)

```{r,echo=F}

aux = bind_rows(
  mod2_permu,
  mod4_permu,
  mod6_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

@@

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")

aux <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux) %>%
  kable_styling(position = "center")

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)

aux <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux) %>%
  kable_styling(position = "center")

@@

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")

aux <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux) %>%
  kable_styling(position = "center")

@@

```{r, echo=F, warning=F}
mod = permutest(mod, progbar = F)

aux <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(aux) %>%
  kable_styling(position = "center")
